Conditional Power and Friends: The Why and How of (Un)planned, Unblinded Sample Size Recalculations in Confirmatory Trials

### 2020-10-13 latex/manuscript.tex
...
added code links

% other
\usepackage{color}
\usepackage[numbers,super,sort&compress]{NJDnatbib}
\bibliographystyle{WileyNJD-AMA}
\usepackage{scalerel}
\newcommand{\kr}[1]{{\color{red}#1}}
\usepackage{comment}

@@

%\begin{comment}
\author{
    Kevin Kunzmann \thanks{
        MRC Biostatistics Unit, University of Cambridge,
        Cambridge Institute of Public Health,
        Forvie Site, Robinson Way,
        Cambridge Biomedical Campus,
        Cambridge CB2 0SR,
        United Kingdom,
        \texttt{kevin.kunzmann@mrc-bsu.cam.ac.uk}
    }\\
    MRC Biostatistics Unit \\
    University of Cambridge \\
    Michael J. Grayling \\
    Population Health Sciences Institute \\
    Newcastle University \\
    Kim May Lee \\
    Pragmatic Clinical Trials Unit\\
    Queen Mary University of London\\
    David S.\ Robertson \\
    MRC Biostatisics Unit\\
    University of Cambridge\\
    Kaspar Rufibach \\
    Methods, Collaboration, and Outreach Group (MCO) \\
    Department of Biostatistics\\
    F. Hoffmann-La Roche, Basel\\
    James M. S. Wason \\
    Population Health Sciences Institute \\
    Newcastle University\\
    and \\
     MRC Biostatistics Unit \\
    University of Cambridge
}
%\end{comment}
%\author{}

@@

>>>>

% other
\usepackage{color}
\usepackage{hyperref}
\usepackage[numbers,super,sort&compress]{NJDnatbib}
\bibliographystyle{WileyNJD-AMA}
\usepackage{scalerel}
\newcommand{\kr}[1]{{\color{red}#1}}
\usepackage{comment}

@@

\begin{comment}
\author{
    Kevin Kunzmann \thanks{
        MRC Biostatistics Unit, University of Cambridge,
        Cambridge Institute of Public Health,
        Forvie Site, Robinson Way,
        Cambridge Biomedical Campus,
        Cambridge CB2 0SR,
        United Kingdom,
        \texttt{kevin.kunzmann@mrc-bsu.cam.ac.uk}
    }\\
    MRC Biostatistics Unit \\
    University of Cambridge \\
    Michael J. Grayling \\
    Population Health Sciences Institute \\
    Newcastle University \\
    Kim May Lee \\
    Pragmatic Clinical Trials Unit\\
    Queen Mary University of London\\
    David S.\ Robertson \\
    MRC Biostatisics Unit\\
    University of Cambridge\\
    Kaspar Rufibach \\
    Methods, Collaboration, and Outreach Group (MCO) \\
    Department of Biostatistics\\
    F. Hoffmann-La Roche, Basel\\
    James M. S. Wason \\
    Population Health Sciences Institute \\
    Newcastle University\\
    and \\
     MRC Biostatistics Unit \\
    University of Cambridge
}
\end{comment}
\author{}

@@

\subsection*{Data Availibility Statement}
Data sharing is not applicable to this article as no datasets were generated and
the research is entirely theoretical.
The source code is available at
\href{https://github.com/kkmann/unblinded-sample-size-adaptation}{github.com}
and
\href{https://doi.org/10.5281/zenodo.3925752}{zenodo.org}.
